\texttt{mimix}: Reference-based imputation of missing data

### 2021-03-03 paper/paperRmimix.tex
Add text on covariates

\title{mimix: Reference-based imputation of missing data}
\author{by Ian R White, Kevin McGrath, Matteo Quartagno, Suzie M Cro and James Carpenter}

@@

\abstract{
Reference-based imputation is a multiple imputation technique which imputes quantitative outcome data that are missing after participant discontinuation of allocated treatment in a randomised trial.
We present and describe an R package, mimix, for performing reference-based imputation, including a causal model variant, and we compare its implementation with that in SAS and Stata.
}

@@

% Aims of paper
We have implemented the RBI methods in a new R package, which includes the a full implementation of the causal model. 
The causal model was previously specified for a two-arm trial and has been extended here for a multi-arm trial.
The aim of this paper is to describe our implementation of mimix in R, to illustrate its use, and to describe its novel features by comparison with the implementations in SAS and Stata.

@@

@@

Covariates are handled ... [HOW? IAN THINK]

@@

The program is based on Suzie Cro’s Stata program mimix.

>>>>

\title{\texttt{mimix}: Reference-based imputation of missing data}
\author{by Ian R White, Kevin McGrath, Matteo Quartagno, Suzie M Cro and James Carpenter}

@@

\abstract{
Reference-based imputation is a multiple imputation technique which imputes quantitative outcome data that are missing after participant discontinuation of allocated treatment in a randomised trial.
We present and describe an R package, \texttt{mimix}, for performing reference-based imputation, including a causal model variant, and we compare its implementation with that in SAS and Stata.
}

@@

% Aims of paper
We have implemented the RBI methods in a new R package, which includes the a full implementation of the causal model. 
The causal model was previously specified for a two-arm trial and has been extended here for a multi-arm trial.
The aim of this paper is to describe our implementation of \texttt{mimix} in R, to illustrate its use, and to describe its novel features by comparison with the implementations in SAS and Stata.

@@

[ADD SOMETHING ON INDIVIDUALS WITH NO OBSERVED VALUES?]

@@

Covariates are used to improve the plausibility of MAR assumptions and to improve the precision of imputed values \citep{ian:MItutorial}. 
In \texttt{mimix}, they are included in the multivariate normal model fitting as part of the variable $Y_0$. [KEVIN IS THIS CORRECT? MIGHT THEY BE WRONGLY CARRIED FORWARD UNDER LMCF?]

Missing values in covariates are not allowed in \texttt{mimix}. For these missing values in the randomised setting, single imputation methods are preferred, so mean imputation or the missing indicator method should be used before calling \texttt{mimix} \citep{ian:MIinRCTs}.

@@

The program is based on Suzie Cro’s Stata program \texttt{mimix}.
